---
title: "Homework #10"
author: "NETID"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

 
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 200, fig.cap = NULL, message = FALSE, warning=FALSE, error = TRUE)
library(stringr)
library(ggplot2)
library(tibble)
library(lubridate)
library(openintro) 
load("Lab09.RDATA")
ekosol <- TRUE
```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should :

  a. have made use of only functions listed in lab, or previous labs.
  b. have each problem on a different page.
  c. have any computed values displayed either inline or explicitly at the end of a code chunk.
  d. not be done by brute force or by inspection. These are methods where the source data is inspected, and the solution dataframe/vector is constructed by explicitly typing in the correct data values. Methods should be scalable. They should work for a dataset with 10 values or 10,000,000 values.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)

**Instructions:**

  1. Recreate the given graphs. 
  2. Use either the dataframe indicated in the title or create the dataframe if there is no dataframe given in the title.
  3. All individual plotted points have integer values. (If it looks like it is close to (2,1), then the plotted point is at (2,1) )
  4. If the size of a point appears to be different from the default, the size does not need to be matched exactly. Relative size is all that should be maintained.
  5.The only colors that will be specifically set/specified are: "black", "blue", "orange", "red", "grey50". Any other color is a natural selection of an aesthetic mapping.
  6. Give each graph a 'more descriptive' title
  
   

\newpage

Problem 1: Display all strings in the **sentences** vector that end with a digit.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage


Problem 2: Display all strings in the **sentences** vector that do not start with an uppercase letter.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage

Problem 3: A **consecutive pair** of a leTTer is an oCCurence were a leTTer aPPears twice in a row.  Find all strings that contain at least two consecutive pairs of the same letter. The first sentence of this question satifies this. The letter T shows up as a pair twice. The second sentence of this problem as some consecutive letters, but the pairing does not show up more than once. Use the **sentences** vector.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage


Problem 4: Display all strings in the **sentences** vector that do not do not contain a lower case r, s or t.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage


Problem 5: Display all strings in the **words** vector that start with a vowel, contain q and end with a consonant.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage


Problem 6: Display all strings in the **words** vector that start with a vowel, contain q and end with a consonant.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage

Problem 7: Display all strings in the **words** vector that are ten or eleven letters long.

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```


\newpage

Problem 8: Display all strings in the **words** vector that start and end with the same two letters, in reverse order..

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```


\newpage

Problem 9: Display all strings in the **sentences** vector whose last full word is "cat".

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```

\newpage


Problem 9: Display all strings in the **colors()** function does not contain any of the following color names followed by a digit:

  a. brown
  b. white
  c. light
  d. dark
  e. blue
  f. grey or gray
  g. green
  

```{r echo = ekosol, fig.height = 8, fig.width = 16}
# Show your work here




```






