---
title: 'Lab #7'
author: "pav35"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
---

 
 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, dpi =200, fig.cap = NULL, message=FALSE, warning=FALSE)
library(stringr)
library(ggplot2)
library(openintro) # You need to install this package


```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should :

  a. have made use of only functions listed in lab, or previous labs.
  b. have each problem on a different page.
  c. have any computed values displayed either inline or explicitly at the end of a code chunk.
  d. not be done by brute force or by inspection. These are methods where the source data is inspected, and the solution dataframe/vector is constructed by explicitly typing in the correct data values. Methods should be scalable. They should work for a dataset with 10 values or 10,000,000 values.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)
  
**Instructions for Graphs:**

  1. Recreate the given graphs.
  2. Use either the dataframe indicated in the title or create the dataframe if there is no dataframe given in the title.
  3. Add a new variable to each dataframe. Its values will be dependent on another variable in the dataframe.
  4. If the size of a point appears to be different from the default, the size does not need to be matched exactly. Relative size is all that should be maintained.
  5.The only colors that will be specifically set/specified are: "black", "blue", "orange", "red", "grey50". Any other color is a natural selection of an aesthetic mapping.
  6. Give each graph a 'more descriptive' title
  7. Solutions should not be typed in a lab. If a solution is accidentally included, you should inform the instructor. Copying a solution is a form of academic dishonesty. 
  
  




\newpage

Problem 1: Write an if... else... statement that will decide if the given value for $x$ is greater than 1. If the value is greater than one, print "YAHOO", otherwise print "bummer"

```{r }
x  <- 1843%%19
# Show your work here
if(x> 1){
  print("Yahoo!")
}

```


\newpage


Problem 2: Use the switch function to display a string based on the value of the given value $x$. If $x$ is the letter A, display "YAHOO". If $x$ is the letter B, display "bummer". Otherwise, display nothing but an empty string.

```{r }
x  <- sample( letters, 1)
# Show your work here

switch(EXPR = x, a = "Yahoo", b = "bummer", " ")

```
\newpage

Problem 3: Refer to the mariokart dataset. Use the ifelse() function to create a new variable. Its values should indicate if wheels were included with the purchase. The new variable should be made part of the mariokart dataframe. Recreate the graph.

```{r }
# Show your work here
mariokart

mariokart["included"] = ifelse(mariokart$wheels > 0, "Yes", "no")

ggplot(data = mariokart, mapping = aes(x = seller_rate, y = total_pr, color = included) ) + geom_point(color = "black") + geom_smooth() + labs( x = "Number of Selling Ratings", y = "Total Price", title = "Mario Kart")
```



\newpage



Problem 4: Refer to the possum dataset. Use a for loop and an if...else..statement to create a new variable young.or.old.  Its values should indicateif a possum was considered young(<2.25) or old. The new variable should be made part of the possum dataframe. Recreate the graph.

```{r }

remove(possum)
possum<-possum[ complete.cases( possum ),]
possum$young.or.old  <- NA
ln <- dim(possum)[1]
# Show your work here
```




```{r, error = TRUE}

for( i in 1:ln){
  age <- possum$age[i]v
  if(age<2.25){
    possum$young.or.old[i] <- "young"
  }else {
    possum$young.or.old[i] <- "old"
  }
}

ggplot(data=possum, mapping = aes( x = sex, y = total_l, color = young.or.old, size = tail_l))+
  geom_jitter(alpha = .5)+
  labs(title = "possum", x = "Sex", y= "Total Length", 
       color = "Younger than 2.25 years?")
 

```



