---
title: "Homework #7"
author: "pav35"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

 
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 200, fig.cap = NULL, message = FALSE, warning=FALSE)
library(stringr)
library(ggplot2)
library(tibble)
library(openintro) # You need to install this package

```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should :

  a. have made use of only functions listed in lab, or previous labs.
  b. have each problem on a different page.
  c. have any computed values displayed either inline or explicitly at the end of a code chunk.
  d. not be done by brute force or by inspection. These are methods where the source data is inspected, and the solution dataframe/vector is constructed by explicitly typing in the correct data values. Methods should be scalable. They should work for a dataset with 10 values or 10,000,000 values.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)

**Instructions:**

  1. Recreate the given graphs. 
  2. Use either the dataframe indicated in the title or create the dataframe if there is no dataframe given in the title.
  3. All individual plotted points have integer values. (If it looks like it is close to (2,1), then the plotted point is at (2,1) )
  4. If the size of a point appears to be different from the default, the size does not need to be matched exactly. Relative size is all that should be maintained.
  5.The only colors that will be specifically set/specified are: "black", "blue", "orange", "red", "grey50". Any other color is a natural selection of an aesthetic mapping.
  6. Give each graph a 'more descriptive' title
  
   

\newpage

Problem 1: Using the given vector $x$, find the absolute value of the difference of consecutive elements. The result should be a vector named result. Use a for loop.

```{r }
x <- c( 1, 41, 82, 49, 65, 12, 76, 13, 18, 9, 96, 91, 22, 24, 48, 100, 38, 64, 19, 83, 85, 62, 78, 29, 61, 95, 6, 21, 28, 15, 45, 43, 97, 56, 93, 81, 87, 88, 52, 60, 79, 5, 94, 46, 66, 11, 14, 75, 59, 67, 63, 98, 23, 44, 8, 70, 27, 7, 69, 50, 55, 26, 4, 36, 2, 47, 40, 73, 35, 42, 74, 72, 54, 90, 68, 30, 84, 20, 51, 92, 25, 37, 57, 86, 53, 3, 33, 10, 16, 89, 32, 58, 34, 99, 17, 77, 71, 31, 39, 80)
ln <- length(x)
result <- rep( NA, times = ln-1)
# Show your work here
result = x

for (index in 1:length(x)) {
  result[index] = abs(result[index+1] - x[index])
}

print(result)

```






\newpage

Problem 2: Using a for loop, determine the average of resulting vector from Problem 1.

```{r }
# Show your work here
res = result[1: length(result) - 1]
sum = 0
for (i in 1:length(res)){
  sum = res[i] + sum
}
average = sum/length(res)
print(sum)
```




\newpage

Problem 3: Using a for loop, determine the product of the elements of the vector $x$.

```{r }
x <- c(0.73, 0.95, 3.92, 3.78, 0.14, 0.89, 1.07, 3.26, -0.21, 0.39, -0.49, 1.16, -0.6, 1.18, 0.7, -0.79, -0.6, 2.59, 2.3, 3.57, 3.28, 3.94, 1.54, 2.1, 1.2, 1.21, 3.13, 3.5, 0.3, 2.94, 1.52, -0.42, 1.91, 0.02, 3.19, 3.72, 0.21, -0.43, 0.45, 2.37, 3.22, 3.45, 0.09, 3.9, -0.56, 0.56, -1, 0.04, 3.23, 0.3)
# Show your work here

for (val in 1:length(x)) {
  product = (val * val+1)
}
print(product)
```

\newpage


Problem 4: Use a for loop and if..else.. statements to create a new variable for the babies dataframe that will allow you to recreate the following graph.

```{r message=FALSE, warning=FALSE,fig.height = 4, fig.width =8, out.height=500}
remove(babies)
cc <- complete.cases(babies$age)
babies<-babies[cc,]
babies$age_group = c()
# Show your work here

for (index in 1:length(babies$age)){
  if (babies$age[index] <= 23) {
 babies$age_group[index] =  "23 and below"}
  else if (babies$age[index] > 23 & babies$age[index] <= 26){
 babies$age_group[index] = "26 and below, above 23"}
  else if ((babies$age[index] > 26) & (babies$age[index] <= 31)) 
    babies$age_group[index] = "31 and below, above 26"
  else if (babies$age[index] > 26)
    babies$age_group[index] = "above 26"}
  

ggplot(data = babies, mapping = aes(x = gestation, y = bwt, color = babies$age_group )) + geom_point() + stat_smooth(se = FALSE) + labs(title = "Babies Born By Parents Age", x= "Gestation", y = "Birth Weigth", legend = "Age Group")

```




\newpage

Problem 5: 

```{r }
# Show your work here
ggplot(data = cpu, mapping = aes(y = base_clock,  fill = company)) + geom_bar(orientation = "y", width = .06, position = "dodge") + labs(title = "CPU DATA", x = "Frequency", y = "Base Clock ( GHz )")
```




\newpage


Problem 6: 

```{r message=FALSE, warning=FALSE}
# Show your work here
# wrap the date variable in the ymd() function

library(lubridate)


ggplot(data = goog, mapping = aes(x = ymd(date), y = open)) + geom_point(color = "blue", size =3) + geom_path(mapping = aes(color = close)) + geom_path(maping = aes(color = open)) + geom_hline(yintercept = 750, lty=2) 
```



\newpage


Problem 7: Use the Rubber dataframe to recreate the following graph. A new variable should be created using the ifelse function. It should classify tensile  strenght as either Low or High

```{r message=FALSE, warning=FALSE}
# Show your work here

library(MASS)
Rubber
Rubber.tensile_str = c()
mean_tens = mean(Rubber$tens)

for (index in 1:length(Rubber)){
  if (Rubber$tens[index] >= mean_tens){
    Rubber.tensile_str[index] = "High"}
  else if (Rubber$tens[index] < mean_tens) {
    Rubber.tensile_str[index] = "Low"}
}
ggplot(data = Rubber, mapping = aes(x = hard, y = loss)) +  geom_point(shape = 2, fill = "blue", color = "blue") + geom_smooth(color = "red") + labs(title = "Rubber Data Frame", x = "Hardness", y = "Abrasian Loss")
```



\newpage

Problem 8(graduate): Recreate the graph

```{r fig.height = 6, fig.width =12, out.height=500}
# Show your work here


```


