---
title: 'Lab #11'
author: "pav35"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
---

 
 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, dpi =200, fig.cap = NULL, message=FALSE, warning=FALSE)
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(openintro) 
library(tidyr)
load("Lab11.RDATA")
# You need to install this package
ekosol <- TRUE

```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should :

  a. have made use of only functions listed in lab, or previous labs.
  b. have each problem on a different page.
  c. have any computed values displayed either inline or explicitly at the end of a code chunk.
  d. not be done by brute force or by inspection. These are methods where the source data is inspected, and the solution dataframe/vector is constructed by explicitly typing in the correct data values. Methods should be scalable. They should work for a dataset with 10 values or 10,000,000 values.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)
  

\newpage

Assuming that the **who.tidy** dataframe is tidy, each problem requires taking a 'messy' dataframe and making it tidy like **who.tidy**.

```{r}
who.tidy
```


Problem 1: Make **who2** look like **who.tidy**. Reassigning **who.tidy** to **who2** will receive no credit.

```{r echo = ekosol}
who2
# Show your work here

pivot_wider(data = who2, id_cols = country, names_from = type, values_from = count)


```


\newpage

Problem 2: Make **who3** look like **who.tidy**. Reassigning **who.tidy** to **who3** will receive no credit.

```{r echo = ekosol}
who3
# Show your work here

separate(data = who3, col = rate, into = c('cases', 'population'))

```



\newpage

Problem 3: Use **who4a** and **who4b** to recreate **who.tidy**. Assigning **who.tidy** as your answer will receive zero credit.

```{r echo = ekosol}
who4a
who4b
# Show your work here


new = full_join(who4a, who4b, by = 'country')
```


\newpage

Problem 4: Use **who5** to recreate **who.tidy**. Assigning **who.tidy** as your answer will receive zero credit.

```{r echo = ekosol}
who5
# Show your work here

unite(data = who5, col = year, century, year, sep = "" )
separate(data = who5, col = rate, into = c('cases', 'population'))

```
