---
title: "Lab #4"
author: "NETID"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

 
 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(ggplot2)


```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should :

  a. have made use of only functions listed in lab, or previous labs.
  b. have each problem on a different page.
  c. have any computed values displayed either inline or explicitly at the end of a code chunk.
  d. not be done by brute force or by inspection. These are methods where the source data is inspected, and the solution dataframe/vector is constructed by explicitly typing in the correct data values. Methods should be scalable. They should work for a dataset with 10 values or 10,000,000 values.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)
 

\newpage


Problem 1: Construct a dataframe for each of the following sets of specifications.  The construction of each should not be done by brute force ( listing out elements). 

  a. Name: example.dataframe.1, 
  b. Four variables with 10 observations each. 
  c. variable.1 contains ten replications of the string 1.
  d. variable.2 contains numbers 1 - 10 in increasing order.
  e. variable.3 contains ten $TRUE$ values.
  f. variable.4 contains the first 10 colors from the colors function.


 
```{r}
# Show your work here:
variable_1 = rep("1", times = 10)
variable_2 = c(1:10)
variable_3 = rep(TRUE, times = 10)
variable_4 = colors()[1:10]
dat1 = data.frame(variable_1)
dat2 = data.frame(variable_2)
dat3 = data.frame(variable_3)
dat4 = data.frame(variable_4)


```




\newpage


Problem 2: How many rows and columns do the dataframe have? This should be done with a function, not by inspection.

  a. ChickWeight


```{r}
# Show your work here:


dim(ChickWeight)

```




\newpage

Problem 3: Extract the following from the indicated dataframe: (This should not be done by inspection.)

```{r}

# Loblolly: The age variable
# Show your work here

Loblolly$age



```



\newpage




Problem 4: Extract the following from the indicated dataframe: (This should not be done by inspection.)

```{r}
# Loblolly: Rows with heights over 60 ft
# Show your work here

Loblolly[Loblolly$height > 60, ]


```


\newpage


Problem 5: Add an extra column to the **Formaldehyde** data frame. It should be called **double.optden**. Its values should be double the values of the **optden** variable.  (Each value should not be individually computed and placed in a vector. The values should all be created as a function of the original **optden** vector as a whole.) Show the new structure of Formaldehyde.


```{r}

Formaldehyde$"double.optden" = Formaldehyde$optden * 2

Formaldehyde

```


\newpage


Problem 6: Recreate the following graphs using the dataframe indicated in the title. (Do not worry about recreating the title)

```{r }
# Show your work here

loblolly_graph = ggplot(data = Loblolly, mapping = aes( x = age, y = height)) + geom_point( )

loblolly_graph



```


