---
title: "Homework #4"
author: "pav35"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

 
 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(ggplot2)

```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should :

  a. have made use of only functions listed in lab, or previous labs.
  b. have each problem on a different page.
  c. have any computed values displayed either inline or explicitly at the end of a code chunk.
  d. not be done by brute force or by inspection. These are methods where the source data is inspected, and the solution dataframe/vector is constructed by explicitly typing in the correct data values. Methods should be scalable. They should work for a dataset with 10 values or 10,000,000 values.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)
 

\newpage

Problem 1: Construct a dataframe for each of the following sets of specifications.  The construction of each should not be done by brute force ( listing out elements). 

  a. Name: example.dataframe, 
  b. Three variables with 78 observations each. 
  c. variable.1 contains the letters of the lowercase alphabet each repeated 3 times consecutively. 
  d. variable.2 contains numbers 1 - 78 in decreasing order.
  e. variable.3 contains the last 78 colors in the colors() function. Starting with the last in the list alphabetically.


 
```{r}
# Show your work here
variable.1 = rep(letters, each = 3)
variable.2 = seq(from = 78, to = 1)
variable.3 = sort(colors())[(657-77):657] 
example.dataframe = data.frame(variable.1, variable.2,variable.3)

example.dataframe





```




\newpage


Problem 2: How many rows and columns do the dataframe have? This should be done with a function, not by inspection.

  a. Formaldehyde
  b. Loblolly
  
  

```{r}
# Show your work here

print(dim(Formaldehyde))
print(dim(Loblolly))

```
 




\newpage

Problem 3: Extract the following from the indicated dataframe: (This should not be done by inspection.)

```{r}

# Formaldehyde: The optical density variable ( Use a name, and show only entries 3 and 4) 
# ChickWeight:  The weight variable ( Use indexes show only entries 15, 16, 19, 40)
# Show your work here


optical_density = Formaldehyde$"optden"[3:4]


chicken_weight = ChickWeight$"weight"[c(15,16,19,40)]

print( optical_density)

print(chicken_weight)

```



\newpage




Problem 4: Extract the following from the indicated dataframe: (This should not be done by inspection.)

```{r}
# Formaldehyde: Rows with carb over 0.5 ml
# ChickWeight:  Rows at age 0 days.
# Show your work here

Formaldehyde$carb[Formaldehyde$carb > .5]


ChickWeight[ChickWeight$Time == 0,]

```


\newpage


Problem 5: Recreate the following graphs using the dataframe indicated in the title. (Do not worry about recreating the title)

```{r }
# Show your work here

tree_plot = ggplot(data = trees) + geom_point(mapping = aes(x = Volume, y = Height, color = Girth)) + scale_fill_manual(values = c("blue")) + xlab("Volume") + ylab("Height") + labs(title = "Trees")

tree_plot


#quakes
#+ scale_fill_manual(values = c("blue", "grey50")) 

quakes_plot = ggplot(data = quakes, mapping = aes(x = depth, y = mag, color = mag, depth)) + geom_point(size = 5, alpha = .25) + xlab("depth") + ylab("mag") + labs(title = "Quakes") 
quakes_plot
```







\newpage


Problem 6: (GRADUATE) Extract the following from the indicated dataframe: (This should not be done by inspection.)

```{r}
# Loblolly: The age of all Loblolly pine trees with a height over 55 ft.
# ChickWeight:  The weight of chicks at 4 days old.
# Show your work here


age_over55 = Loblolly$age[Loblolly$height > 55]

weight_over_4days = ChickWeight$weight[ChickWeight$Time >= 4]

print(age_over55)

print(weight_over_4days)
```




\newpage


Problem 7: (GRADUATE) Sort the rows/observations of the ChickWeight dataframe. The weight variable entries should be increasing.   (This should not be done by inspection.)

```{r}
# Show your work here
# library(dplyr)
# arrange(ChickWeight, weight)

chicken_weight_ascending =  ChickWeight[order(ChickWeight$weight),] 

```
