---
title: "Lab #3"
author: "pav35"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

 
 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(stringr)
```

 
 
Things to complete: 

  a. All examples completed by the TAs
  b. All of the problems assigned to you

Each problem should have:

  a. made use of only functions listed in lab, or previous labs.
  b. each problem on a different page.
  c. any computed values displayed either inline or explicitly at the end of a code chunk.
    
Thing to turn in:

  a. One PDF (produced from a knitted word document.)
 

\newpage


Problem 1:  Determine the type of vector for each of the following: integer, double, character, logical


```{r echo = T, eval = T}
#Show your work here.

#a. <- 
  one_a = c(T, T, T, T, "F")
  typeof(one_a)

#b. 
  one_b = c(T, 1)
  typeof(one_b)


```



\newpage


Problem 2: Create the following vectors and assign a variable to the result

  a. Nine evenly spaced elements starting at -0.123 and ending at 68




```{r}
#Show your work here.

two_vector = seq(from = -0.123, to = 68, length.out = 9 )
print(two_vector)

```


\newpage


Problem 3: Determine the number of elements in the following vectors.
 

```{r echo = T, eval = T}
#Show your work here.
x <- seq(from = 156, to = 10000, by = pi)
length(x)


```

\newpage


Problem 4: Use the given vectors and the $rep()$ to create the indicated vector:

```{r eval =FALSE, echo =T}
   
[1] "girl" "boy"  "girl" "boy"  "girl" "boy"  "girl" "boy"  "girl" "boy"  
[11] "girl" "boy"  "girl" "boy"  "girl" "boy"  "girl" "boy"  "girl" "boy"
   
```

```{r echo = T, eval = T}
a <- c("girl", "boy")
x <- 1
y <- 4:7
z <- c(0, 0, 0, 0)
#Show your work here.

rep(a, length(c(x,y,z,x)))


```
\newpage







Problem 5: Create the following matrix:

```{r eval =FALSE, echo=TRUE}
     [,1] [,2] [,3] [,4] [,5] [,6]
[1,] "a"  "b"  "c"  "d"  "e"  "f" 
[2,] "g"  "h"  "i"  "j"  "k"  "l" 
[3,] "m"  "n"  "o"  "p"  "q"  "r" 
[4,] "s"  "t"  "u"  "v"  "w"  "x" 
```

```{r echo = T, eval = T}
#Show your work here.

# Create a vector with just the desired letters.
dat = letters[1:24]
print(dat)
# Use the vector to create a matrix. Make note of the number of rows and colums as well as how they are filled in.
letter_matrix = matrix(data = dat, nrow = 4, ncol = 6, byrow = TRUE )
print(letter_matrix)

```

\newpage


Problem 6: Extract all values in the fifth row of the matrix

```{r echo = T, eval = T}
#Show your work here.
mat <- matrix(fruit, nrow = 16)
#print(mat)
print(mat[,5])


```



\newpage


Problem 7: Determine if any of the values in the vector $x$ are equal to $\pm$`Inf`

```{r echo = T, eval = T, results= 'hide'}
#Show your work here.

top <- -10001:10002
bottom <- c(7, 121, 117)
x <- 1/(top %/% bottom)

is.infinite(top)

is.infinite(bottom)

is.infinite(x)

```

After running the is.inf command I can see that none of them are equal to plus or minus infinity.



\newpage


Problem 8: Determine if any of the values in the vector $x$ are missing (NA)

```{r echo = T, eval = T, results= 'hide'}
#Show your work here.

# Don't worry about these commands, we will go over them in the future
set.seed(3) 
x <- sample(c(1,NA), size=10000, replace = TRUE, prob = c(.9999,.0001) )
is.na(x)



```
None of the above values are equal to NA according to the is.na command. 