---
title: 'Homework #01'
author: pav35
output:
  word_document: default
  html_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = T, eval=T)

```



Knit your final answers into a word document. Convert that to a PDF. Upload the PDF to Gradescope.

Attach/Match the questions and your answers in Gradescope. Points will be deducted for each question where this is not done.

This homework covers material that can be found up to page 10 in the notes. Do not use functions or operations not listed on those pages.

Graduate questions are required for graduate students. They are extra credit for under graduates. Extra credit can not be used to raise a grade over 100%.

\newpage

1. Determine the following:
 
```{r} 
  #  a.
sqrt(24)
  #  b. 
(sin(6*pi)/tan(7*pi))*(180/pi)
```
    


\newpage
  

2. For each of part, compute a vector that contains the values listed for that part. 

    a. Two squared. Three cubed. Four to the forth. Five fifthed. ... Ten to the tenth.  
    b.The vector containing: The quotient of 5 divided by 3. The quotient of 2 divided by 4. The quotient of 228 divided by 8. The quotient of 323 divided by 8. 
    
```{r}

# a.

bases = c(2,3,4,5,6,7,8,9,10) 
powers = c(2,3,4,5,6,7,8,9,10)
c(bases^powers)
# b. 

```

\newpage

3. Compute the following making use of recycling.( Shrink the given vectors)

    a. c(1, 2, 3, 4, 5, 6) * c( 0, 4, 6, 0, 4, 6) - c(1, 1, 1, 1, 1, 1, 1 )
    b. c(1, 2, 3, 4, 5, 6) * c( 0, 4, 6, 1, 9, 0) - c(1, 1, 1, 1, 1, 1 )

```{r}

# a.
c(1, 2, 3, 4, 5, 6) * c( 0, 4, 6, 0, 4, 6) - c(1, 1, 1, 1, 1, 1, 1 )

c(1,2,3,4,5,6) * c(0,4,6) - 1

# b.

c(1,2,4,5,6) * c(0,4,6,1,9) - 1

```



\newpage
    
4. Compute the following without using recycling.( Expand the given vectors as needed)

    a. c(1, 2) + ( c(0, 10, -1) * 20 )
    b. c(1, 2) / c(1, 2, 1, 2) - c(1, -1, 1, -1, 1, -1)
    
```{r}

# a.

c(1,2,1) + (c(0,10,-1) * c(20,20,20))

# b. 

c(1,2,1,2,1,2) / c(1,2,1,2,1,2) - c(1,-1,1,-1,1,-1)


```


\newpage

5. Create a single variable for each of the following vectors. Use a descriptive name. The naming convention to use is indicated.

    
```{r}

# a.

divide_by_pi = c(0,1,2,3,4,5,6,7,8)/ pi

# b. 

divideBypowers = 1/c(1,2,2^2,2^3,2^4,2^5,2^6,2^7,2^8)

```



\newpage

    
6. Use the given variables to create the indicated vectors. 

```{r}
ones<-c(1,1,1)
evens<-c(2,4,6, 8)
negatives<--c(10,20,30,120) 
```

    a. c(1, 1, 1, 1, 1, 1, 99)
    b. c(1, 1, 1, 2, 4, 6, 8, 10, 20, 30, 120)
    c. c(1,1,1,99,10,20,30,120,10,20,30,120,1,1,1,1,1,1)
    d. c(2,2,2,4,8,12,16)
    e. c(0, 0, 0, 5, 4, 5, 15, 0, 0, 0, 0)
    
```{r}

# a.

c(ones,ones,99)

# b. 

c(ones,evens, -negatives)

# c.

c(ones, 99, -negatives, - negatives, ones, ones)

# d.

c(ones*2, evens*2)

# e.

c(ones-1, -negatives/evens,(evens/evens) -1)
                                                      
```    
    
    
 
\newpage 


7. ( Pythagorean Theorem ) 


```{r}

pyth_theorem = function(hypothenuse, side) {

  other_side = sqrt(hypothenuse**2-side**2)
  print(other_side)
}
 
# pyth_theorem(5,4)

a = sqrt( 5^2 - 4^2)
a
b = sqrt( 13^2 - 12^2)
b
c = sqrt(41^2 - 40^2)
c
d = sqrt(29^2 - 21^2)
d
e = sqrt(65^2 - 63^2)
e

```


\newpage

    
8. ( GRADUATE ) Given Newton's Law of Gravitation 

```{r}

newton_law = function(mass_1,mass_2,radius) {

  g_force = 12.6*((mass_1 * mass_2)/radius^2)
  print(g_force)
}

#newton_law(10,11,2)


part_a = 12.6*((10 * 11)/2^2)
part_a
part_b =12.6*((34 * 21)/.5^2)
part_b
part_c = 12.6*((4 * 39)/19^2)
part_c
part_d = 12.6*((884 * 73)/98^2)
part_d
part_e = 12.6*((4 * 34)/23^2)
part_e

```

\newpage
    
9. ( GRADUATE )Fibonacci Sequence 

I know we haven't covered functions in class but I have been having a lot of fun programming in R so I thought I'd challenge myself with this. 

```{r}

#fib = (psi^n - phi^n)/ sqrt(5)

fibonacci = function(n){
  
  psi = (1 + sqrt(5))/2
  phi = ((1-sqrt(5))/2)
  fib = (psi^n - phi^n)/ sqrt(5)
  print(fib)
  
}

c(fibonacci(0:20))

#Or if I wanted to do it manually. 

psi = (1 + sqrt(5))/2
phi = ((1-sqrt(5))/2)
one_twenty = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)

fib_vect = (psi^one_twenty - phi^one_twenty)/ sqrt(5)
fib_vect
```