---
title: 'Lab #01'
author: "pav35"
date: "8/31/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For 1-4, do not make use of variable assignments. For 5-7, make use of variable assignment. 

1. Determine the following:
  
```{r}

#a. 

19**2.2

#b. 

((19**log(9))/18) + 15 

```
    
\newpage
    
2. Which produce equal/identical results. 

```{r}
# Show your work here

#a) 
c(1**2, 2**3, 4**6, 8**-1)

#b)
c(1*pi, 2*pi,3*pi, 10*pi)

#c)
c(1,2,4,8)**c(2,3,6,-1)

#d)
c(12,5,-4,2) + c(1,2)

#e)
c(10,2,3,1)*pi

#f)
c(12,5,-4,3) + c(1,2,1)

```
Here we have that a == c and d == f. However even though lists b and e have the same members
the order of these lists is different. This would imply that they are not equivalent lists. 

\newpage
    
3. Compute the following making use of recycling.( Shrink the given vectors)

```{r}
# Show your work here

c(1,2,3,4,5,6) * c(0,4,6,0,4,6) - c(1,1,1,1,1,1)

#This list operation can be shortened with the following actions:

c(1:6) *c(0,4,6) - c(1)

```
    
\newpage
    
4. Compute the following without using recycling.( Expand the given vectors as needed)

c(1,2) + c(0, 10,-1)*20 == c(1,2) + c(0, 200,-20), however because the lengths of these lists are different then we must expand the shorter of the two. R does this for us automatically however if we choose not to use recycling then we get: c(1,2,1) + c(0,200,-20)

Here we can check our work:  

```{r}
# Show your work here


# 1)
 
x = c(0,10,-1) * 20

# 2) 

c(1,2,1) + x



```
Now we see that the two operations are equivalent. 

\newpage


5. Create a single variable for each of the following vectors. Use a descriptive name. The naming convention to us is indicated.

```{r}
# Show your work here

# a. 

period.seperated.vector =c(12,144,1728,20736)

# b.

ALLCAPITALSVECTOR = c(1,3,5,7,9,11,13)

```
    
    
\newpage
    
6. Create the following variables, and assign an appropriate vector to it. Modify the variable name to use the indicated naming convention

```{r}
# Show your work here

# a.sqrt.ofTWO ( period separator)

sqrt.of.two = sqrt(2)


# b.naturallogofonethroughten ( Camel Case )

NaturalLogOfOneThroughTen = log(1:10)


# c.sine_of_0_45_90_continuing_to__360_degrees

sine.of.0.45.90.continuing.to.360.degrees = (sin(seq(0,360, by = 45)))*pi/180


```
    
\newpage
    
7. Create a variable for the first vector in part a. Use that vector to compute the vectors that follow.  Assign variable names to each result. Display each result.

```{r}
# Show your work here

# a.

part_a_vector = c(1,2,3,4,5,6,7,8,9,10)

# b.

part_a_vector_times_pi = part_a_vector * pi

# c.

part_a_vector_power_denominator_ = 1 / 3**part_a_vector

# d.

part_a_vector_ones = part_a_vector**0


```
    
\newpage
    
8. Complete the following steps.

    a. In the console, create a vector called TESTER. Assign the c( 3, 1, 4, 1, 5, 9 ) to it.
    b. Check the environment for the variable TESTER and that its value is c( 3, 1, 4, 1, 5, 9 ) 
    c. Create a code chunk with a two lines of code. DO NOT RUN THE CHUNK 
  
TESTER

```{r}

TESTER = 1
TESTER

```

    d. Knit the entire document.
    
    Did the value of TESTER change in the environment? What value for TESTER appeared in your knitted document?
    
Because the code chunk was never ran then the value for the TESTER variable was never updated. This would imply that the value of TESTER is still c(3,1,4,1,5,9) in the console. However whenever a document is knitted all the code chucks or run and updated for the knitted document. This does not affect the values of the variable sin the global enviorment. 